Improving Emotion Detection through Translation of Text to ML Models Trained in Different Languages

### 2023-08-14 paper/appendix/code.tex
Paper Updates | Savings States

Flask is a lightweight and simple to use web framework in Python, allowing developers to create web applications and APIs. Due to it's simplicity and components design, Flask allowed us to rapidly build and interactive web service fro demonstration purposes on this project.
\begin{minted}[fontsize=\small]{python}
# Setup API 
from flask import Flask, request, jsonify
from googletrans import Translator

# Setup
from transformers import DistilBertTokenizer
from pyspark.ml.pipeline import PipelineModel

@@

app = Flask(__name__)
translator = Translator()

@@

@app.route('/predict', methods=['GET'])
def transform_data():
    sentence_en = request.args.get('sentence_en')

    if not sentence_en:
        return jsonify({'error': 'No Sentence (EN) provided!'})

    sentence_de = translator.translate(sentence_en, dest="de").text
    print(f"English: {sentence_en}")
    print(f"German: {sentence_de}")

@@

    #Build Response
    resp = {
        "sentence": {
            "english":sentence_en,
            "german":sentence_de,
        },
        "predictions": {
            "en_rfc": emotions.get(predictions_en_rfc.collect()[0]["prediction"]),
            "en_nb":  emotions.get(predictions_en_nb.collect()[0]["prediction"]),
            "en_lr":  emotions.get(predictions_en_lr.collect()[0]["prediction"]),
            "de_rfc": emotions.get(predictions_de_rfc.collect()[0]["prediction"]),
            "de_nb":  emotions.get(predictions_de_nb.collect()[0]["prediction"]),
            "de_lr":  emotions.get(predictions_de_lr.collect()[0]["prediction"]),
        },
    }

@@

if __name__ == '__main__':
    app.run(host='127.0.0.1', port=8080)
\end{minted}
\clearpage

>>>>

Flask is a lightweight and simple to use web framework in Python, allowing developers to create web applications and APIs. Due to it's simplicity and components design, Flask allowed us to rapidly build and interactive web service fro demonstration purposes on this project.
\begin{minted}[fontsize=\small]{python}
# Setup Spark Session
from pyspark.sql import SparkSession

# Import API Modules 
from flask import Flask, request, jsonify
from flask_cors import CORS
import datetime

# Import Translator
from googletrans import Translator

# Impport Tokenizer and Pipeline Tools
from transformers import DistilBertTokenizer
from pyspark.ml.pipeline import PipelineModel

# Setup Spark Session
sc = SparkSession \
        .builder \
        .master("local[*]") \
        .appName("API-Demo") \
        .getOrCreate()

# Add Numerical Label for Emotions
emotion_key = {
    "boredom": 0,
    "love": 1,
    "relief": 2,
    "fun": 3,
    "hate": 4,
    "neutral": 5,
    "anger": 6,
    "happiness": 7,
    "surprise": 8,
    "sadness": 9,
    "worry": 10,
    "enthusiasm": 11,
    "empty": 12,
    "---": 13
}

@@

app = Flask(__name__)
CORS(app)  # Use the CORS class to enable CORS for the entire app
translator = Translator()

@@

@app.route('/predict', methods=['GET'])
def transform_data():
    start_time = datetime.datetime.now()
    sentence_en = request.args.get('sentence_en')
    sentence_de = request.args.get('sentence_de')

    print(f"English: {sentence_en}")
    print(f"German: {sentence_de}")

    if sentence_en:
        sentence_de = translator.translate(sentence_en, dest="de").text
    elif sentence_de:
        sentence_en = translator.translate(sentence_de, dest="en").text
    else:
        return jsonify({'error': 'No Sentence provided!'})

    print(f"English: {sentence_en}")
    print(f"German: {sentence_de}")

@@

    # Get End Time
    end_time = datetime.datetime.now()
    elapsed_time = (end_time - start_time).total_seconds()

    #Build Response
    resp = {
        "sentence": {
            "english": sentence_en,
            "german": sentence_de,
        },
        "predictions": {
            "en_rfc": emotions.get(predictions_en_rfc.collect()[0]["prediction"]),
            "en_nb":  emotions.get(predictions_en_nb.collect()[0]["prediction"]),
            "en_lr":  emotions.get(predictions_en_lr.collect()[0]["prediction"]),
            "de_rfc": emotions.get(predictions_de_rfc.collect()[0]["prediction"]),
            "de_nb":  emotions.get(predictions_de_nb.collect()[0]["prediction"]),
            "de_lr":  emotions.get(predictions_de_lr.collect()[0]["prediction"]),
        },
        "metadata": {
            "spark": sc.version,
            "datetime": {
                "start": start_time,
                "end": end_time,
                "elapsedInSeconds": elapsed_time,
            }
        }
    }

@@

if __name__ == '__main__':
    app.run(host='127.0.0.1', port=8080)

\end{minted}
\clearpage
